% !TeX root = ..\main.tex

\section{Recommendation/Conclusion}

MongoDB is a powerful NoSQL database that allows developers to create and manage complex data 
models. It is a good choice for applications that need to store a lot of unstructured data and 
require a scalable solution. However, MongoDB is not suitable for every application. The decision 
to use MongoDB depends on the requirements of your application. (MongoDB, 2023)
One of the main advantages of MongoDB is its flexibility. It allows developers to quickly create 
new features and models without worrying about strict schemas and relationships between the data. 
(MongoDB, MongoDB Scaling, 2023)
Another important advantage of MongoDB is its integration with many modern technologies and 
frameworks. MongoDB provides drivers for many programming languages and is also available on many 
cloud platforms, making implementation easier and faster. (MongoDB, 2023)
MongoDB is a popular NoSQL database that can cover many use cases. With its flexible data 
modeling, scalability, and powerful query capabilities, MongoDB is an excellent choice for 
modern applications that need to store and process large amounts of unstructured data. 
(MongoDB, 2023)
Furthermore, MongoDB has also developed a cloud-based platform called Atlas that allows customers 
to host and manage their MongoDB instances in the cloud. Atlas also provides features such as 
automatic scaling and backups that make managing MongoDB databases easier. (MongoDB, 2023)
Overall, MongoDB is a powerful and forward-looking database that is suitable for many use cases 
and is continuously evolving to meet the requirements of modern applications.


\subsection{Conclusion}

9.2.1 Analytics
MongoDB is also an excellent choice for analytics platforms. The database is highly scalable 
and powerful, allowing for fast processing of large amounts of data (MongoDB, 2023). 
Some examples of big data applications that use MongoDB are:
Analytics tools, log analysis, data warehousing systems.

9.2.2 IoT Applications
MongoDB is also well-suited for IoT applications, as it can quickly and efficiently collect and 
store many data points. The database is easy to implement and scale, making it an excellent 
choice for applications that need to collect a lot of data from a variety of devices 
(MongoDB, 2023). Some examples of IoT applications that use MongoDB are:
Smart home systems, Industry 4.0 applications.

9.2.3 E-commerce Applications
MongoDB can also be useful for e-commerce applications, as it allows for fast transaction 
processing and provides flexible data modeling (MongoDB, 2023). Some examples of e-commerce 
applications that use MongoDB are:
Online marketplaces, e-commerce platforms, payment systems.

9.2.4 Mobile Applications
MongoDB is also well-suited for mobile applications, as it is lightweight and scalable and allows 
for fast data processing (MongoDB, 2023). Some examples of mobile applications that use MongoDB 
are:
Mobile games, messaging apps, fitness apps.


% CAP should be in the conclusion

\subsection{Recommendations for specific use cases}

